Slavnov products and KP tau functions

### 2025-04-11 draft.tex
start calculating the BA function

We can show, see~\cite{Araujo:2021ghu} for a detailed proof of this
statement, that the tau function~\ref{eq:tau-function} admits an
integral representation of the form (ignoring the signs dependence on
the length \(n\) of the spin chain)
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) = 
    \det_{j,k}\left(
    \oint \frac{d w}{2\pi i} e^{\bm{\xi}(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
    \right)
\end{equation}
where 
\begin{equation}
  \bm{\xi}(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; .
\end{equation}
One of the advantages of this representation is that now it makes
sense to consider the limit of the infinite chain, \(n\to \infty\).

@@

It seems that we can consider a basis of functions \(\mathcal{Y}_j(z)\) for the Baker-Akhiezer
functions. I think that this object might say something interesting. In particular, we can
explicitly build solutions of the KP equation. In fact, the functions \(\mathcal{Y}_j\)
above have poles at the Bethe roots, it is interesting. 
\begin{itemize}
\item[\faCheck] What is the pole and root structure of the tau and Baker-Akhiezer (BA) functions?
  In particular, what happens at the Bethe roots?
\item[\faCheck] Basis tau functions
\item[\faCheck] Write the cases n=2 and n=3
\item[\faCheck] What the general case for all \(z_k\) approaching to a single
  value \(w\). 
\item[\faCheck] Write these tau functions in terms of Miwa coordinates
\item It turns out that the Baker-Akhiezer function is the appropriate object to discuss
  the Bethe roots. 
  \item I think that these tau functions come from algebro geometric tau functions. 
  \item I can try to study the dynamics closer to the Bethe roots, I think that the
    \(\Omega\)'s will have some interesting expansions, some of them might vanish. 
  \item This might become a Riemann Hilbert problem
  \item Are these tau functions associated to the Calogero-Moser model??
  \item Elliptic case - see slavnov, zabrodin's paper
\end{itemize}

>>>>

We can show, see~\cite{Araujo:2021ghu} for a detailed proof of this
statement, that the tau function~\ref{eq:tau-function} admits an
integral representation of the form (ignoring the signs dependence on
the length \(n\) of the spin chain)
\todo{\tiny I need to do this calculation carefully now. The contour that gives the
  representation below should avoid the Bethe root \(v_k\), otherwise, we pick
poles we want to avoid.}
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) = 
    \det_{j,k}\left(
    \oint \frac{d w}{2\pi i} e^{\bm{\xi}(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
    \right)
\end{equation}
where 
\begin{equation}
  \bm{\xi}(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; .
\end{equation}
One of the advantages of this representation is that now it makes
sense to consider the limit of the infinite chain, \(n\to \infty\).

@@

It seems that we can consider a basis of functions \(\mathcal{Y}_j(z)\) for the Baker-Akhiezer
functions. I think that this object might say something interesting. In particular, we can
explicitly build solutions of the KP equation. In fact, the functions \(\mathcal{Y}_j\)
above have poles at the Bethe roots, it is interesting. 
\begin{itemize}
\item[\faCheck] What is the pole and root structure of the tau and Baker-Akhiezer (BA) functions?
  In particular, what happens at the Bethe roots?
\item[\faCheck] Basis tau functions
\item[\faCheck] Write the cases n=2 and n=3
\item[\faCheck] What the general case for all \(z_k\) approaching to a single
  value \(w\). 
\item[\faCheck] Write these tau functions in terms of Miwa coordinates
\item I need to calculate the Baker-Akhiezer function for this model using the Japanese formula
  in terms of tau functions. The tau functions above is know. I think that this BA function
  will be similar to the soliton-like solution discussed in section 3.6.2 (page 41) of~\cite{Zabrodin2018}. 
  My functions seem to have a pole of order \(N\) at infinity. And \(N\) zeros at the Bethe roots. 
\item It turns out that the Baker-Akhiezer function is the appropriate object to discuss
  the Bethe roots. 
  \item I think that these tau functions come from algebro geometric tau functions. 
  \item I can try to study the dynamics closer to the Bethe roots, I think that the
    \(\Omega\)'s will have some interesting expansions, some of them might vanish. 
  \item This might become a Riemann Hilbert problem
  \item Are these tau functions associated to the Calogero-Moser model??
  \item Elliptic case - see slavnov, zabrodin's paper
\end{itemize}
